### 2019-12-13 article.tex
model algoritgm started

\begin{figure}
	\includegraphics[width=\linewidth]{images/3dCnn}
	\caption{3D CNN demonstration (kernel size = 3$\times$3$\times$3).}
	\label{fig:CnnSample}
\end{figure}

@@

\begin{figure}
	\includegraphics[width=\linewidth]{images/SarrafParkinsonTestResult}
	\caption{Parkinson's disease diagnosis accuracy and loss using Sarraf and Tofighi's algorithm.}
	\label{fig:SarrafParkinsonTestResult}
\end{figure}

@@

The proposed method can be briefly expressed as Algorithm \ref{alg:proposedMethod}. First of all, input data will be preprocessed using Algorithm \ref{alg:preprocessing}, which removes noises and non-informational data parts (such as the skull). In addition to that, each patient's scan will be normalized to a standard space that boosts the learning phase's efficiency. This step is followed by dividing each sample (containing $t$ 3D fMRI time-slices) to $t$ different images. For instance, in Parkinson's dataset, 30 samples consisted of 198 time-slices of \texttt{$39 \times 64 \times 64$} voxels will turn into $5940$ 3D images. We convert these data to TFRECORD format to improve performance. Furthermore, for each experiment, six participants ($20\%$ of all data) from both groups are randomly selected, and their $t$ time-slices are set aside for the test phase. On the other hand, the rest of the data (which are $24 \times 198$ labeled time-slices) will be shuffled and fed to our 3D deep Bayesian convolutional neural network. We use the first 158 time-slices as training samples while the remnants will be our validation portion of data correspondingly.

@@

Now we can start to train our model based on the proposed architecture which is illustrated in Figure \ref{fig:cnnArch}.

@@

>>>>

\begin{figure*}
	\includegraphics[width=\linewidth]{images/3dCnn}
	\caption{3D CNN demonstration (kernel size = 3$\times$3$\times$3).}
	\label{fig:CnnSample}
\end{figure*}

@@

\begin{figure*}
	\includegraphics[width=\linewidth]{images/SarrafParkinsonTestResult}
	\caption{Parkinson's disease diagnosis accuracy and loss using Sarraf and Tofighi's algorithm.}
	\label{fig:SarrafParkinsonTestResult}
\end{figure*}

@@

First of all, input data will be preprocessed using Algorithm \ref{alg:preprocessing}, which removes noises and non-informational data parts (such as the skull). In addition to that, each patient's scan will be normalized to a standard space that boosts the learning phase's efficiency. This step is followed by dividing each sample (containing $t$ 3D fMRI time-slices) to $t$ different images. For instance, in Parkinson's dataset, 30 samples consisted of 198 time-slices of \texttt{$39 \times 64 \times 64$} voxels will turn into $5940$ 3D images. We convert these data to TFRECORD format to improve performance. Furthermore, for each experiment, six participants ($20\%$ of all data) from both groups are randomly selected, and their $t$ time-slices are set aside for the test phase. On the other hand, the rest of the data (which are $24 \times 198$ labeled time-slices) will be shuffled and fed to our 3D deep Bayesian convolutional neural network. We use the first 159 time-slices ($80\%$) as training samples while the remnants will be our validation portion of data correspondingly.

@@

Now we can start to train our model based on the proposed architecture which is illustrated in Figure \ref{fig:cnnArch}. During the training phase, data gets split to 50 chunks ($95$ samples) which are fed sequentially to the network. Consequently the model can be validated during the training to prevent overfitting and enables us to track the whole process. The proposed method can be briefly expressed as Algorithm \ref{alg:proposedMethod}.

@@

\begin{algorithm}
	\caption{Proposed method}
	\label{alg:proposedMethod}

	\begin{algorithmic}

		\INPUT{processed data which is the output of Algorithm \ref{alg:preprocessing}.}
		\STATE \textbullet~Shuffle scans
		\STATE \textbullet~Put 6 scans (3 group each) aside as test data
		\STATE \textbullet~Split time-slices of data and shuffle them
		\STATE \textbullet~Divide train and validation data to 50 chunks
		\FORALL{50 chunks} 
		\STATE train network (Fig. \ref{fig:cnnArch}) 
		\STATE \hskip1.0em \textbullet~First
		\ENDFOR
		%\IF {$i\geq 5$} 
		%\STATE $i\gets i-1$
		%\ELSE
		%\IF {$i\leq 3$}
		%\STATE $i\gets i+2$
		%\ENDIF
		%\ENDIF 
	\end{algorithmic}

%	\KwData{pre-processed data which is the output of Algorithm \ref{alg:preprocessing}.}
%	\KwResult{trained Bayesian 3D CNN to diagnose Parkinson's disease patients}
%	initialization\;
%	\While{not at end of this document}{
%		read current\;
%		\eIf{understand}{
%			go to next section\;
%			current section becomes this one\;
%		}{
%			go back to the beginning of current section\;
%		}
%	}

\end{algorithm}
